Approximation as Differentiation

### 2025-04-28 main/introduction.tex
Galois slicing citations.

\note{We will use biproducts, and use some results from \cite{karvonen2020}.} % just to generate a bibliography for now

@@

Perera and collaborators introduced the idea of {\em Galois Program Slicing} as a particular conception of program slicing for provenance, described in several publications (FIXME: refs). Galois program slicing forms the basis of Perera's data visualisation tool \href{https://f.luid.org/}{fluid} that allows interactive exploration of programmatically generated visualisations.

>>>>

\note{We will use biproducts, and use some results from \cite{karvonen2020}.}

@@

Perera and collaborators introduced the idea of {\em Galois Program Slicing} as a particular conception of
program slicing for provenance, described in several publications~\cite{perera12a,perera16d,ricciotti17}.
Galois program slicing forms the basis of Perera's data visualisation tool \href{https://f.luid.org/}{Fluid}
that allows interactive exploration of programmatically generated visualisations.
